Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-09-24 tex/paper1/paper1.tex
james edits to the paper

Oscillatory phenomena in the solar corona are relatively rare, both
spatially and temporally.  Two types of oscillatory motions have
received a lot of attention.  The first is known as a transverse
oscillation, since the loop motion is approximately transverse to the
extent of the loop \citep{1999Sci...285..862N}.  These motions appear
to be triggered by nearby flaring events, and are identified with the
fundamental harmonic of the kink mode of the flux tube that comprises
the coronal loop.  The second type is known as a longitudinal
oscillation, or propagating disturbance (PD).  These waves propagate
along flux tubes, and have been identified as slow mode
magnetohydrodynamic (MHD) magneto-acoustic waves (although alternative
interpretations do exist that do not invoke oscillatory phenomena, for
example, \cite{0004-637X-722-2-1013} and \cite{2041-8205-727-2-L37}).

>>>>

Oscillatory phenomena in the solar corona are relatively rare, both
spatially and temporally.  Two types of oscillatory motions have
received a lot of attention.  The first is known as a transverse
oscillation, since the loop motion is approximately transverse to the
extent of the loop \citep{1999Sci...285..862N}.  These motions appear
to be triggered by nearby flaring events, and are identified with the
fundamental harmonic of the kink mode of the flux tube that comprises
the coronal loop.  The second type is known as a longitudinal
oscillation, or propagating disturbance (PD).  These waves propagate
along flux tubes, and have been identified as slow mode
magnetohydrodynamic (MHD) magneto-acoustic waves (although alternative
interpretations do exist that do not invoke oscillatory phenomena, for
example, \citealp*{0004-637X-722-2-1013} and
\citealp*{2041-8205-727-2-L37}).

Other types of oscillatory behavior have been observed.
\cite{2005ApJ...620.1101M} demonstrate the presence of oscillatory
power with periods in the range of 40-80 seconds using high-cadence
H$\alpha$ blue wing observations of a Geostationary Operational
Environmental Satellite (GOES) C9.6-class solar flare obtained at Big
Bear Solar Observatory using the Rapid Dual Imager
\citep{2000SoPh..193..259P, 2007A&A...473..943J}. The measured
properties of these oscillations are consistent with the existence of
flare-induced acoustic waves within the overlying loops.  In addition,
\cite{2013ApJ...772...54A} show that the oscillatory power in the
lower solar atmosphere of active regions increases in response to
flare events at distant solar locations.
